---
title: "Evaluating task and vet sim difficulty."
output: html_document

---

```{r setup_condensed, include=F}
## Load packages here.
library("knitr")
knitr::opts_chunk$set(
  echo = F,
  message   = F, warning = F, error = F,
  results   = "asis",                # Opts: "asis", "markup", "hold", "hide"
  fig.align = "center",              # Opts: "left", "right", "center", "default"
  fig.width = 8, fig.height = 5,
  out.width = "100%",
  fig.pos   = "h", out.extra   = "", # Figures forced closer to chunk location.
  collapse  = TRUE, cache = FALSE, cache.lazy  = FALSE
)
```

# Initialize

```{r init}
library("spinifex")
library("tourr")
library("ggplot2")
library("tibble")

dat <- tourr::rescale(tourr::flea[,1:6])
rb       <- basis_random(n = ncol(dat))
class    <- tourr::flea$species

invisible(capture.output(holes_path <- save_history(dat, tour_path = guided_tour(holes()))))
holes_basis <- as.matrix(holes_path[,, dim(holes_path)[3]])

n <- nrow(dat)
p <- ncol(dat)
k_cl <- length(unique(class))
pca_obj <- prcomp(dat)

pca_var_rate <- pca_obj$sdev^2 / sum(pca_obj$sdev^2)

df_pcaVar <- data.frame(
  pc_number = paste0("PC", 1:p),
  rate_var_explained = pca_var_rate,
  cumsum_rate_var_explained = cumsum(pca_var_rate)
)
```

# Evaluating task -- Rate variables importance to the seperation of 2 clusters.

Consider a sree plot of flea data. This shows which componets are contributing to the *full sample, full dimensionality,* $[n,p]$ variation of the data.

```{r Screeplot}
(g1 <- ggplot(data = df_pcaVar) + 
   ## Individual var bars
   geom_bar(stat = "identity", 
            mapping = aes(x = pc_number, y = rate_var_explained, 
                          fill = "Individual var explained")) + 
   ## Cummulative var line
   geom_line(mapping = aes(x = pc_number, y = cumsum_rate_var_explained,
                           color = "Cumsum of var explained", group = 1),lwd = 1.2) +
   geom_point(mapping = aes(x = pc_number, y = cumsum_rate_var_explained,
                            color = "Cumsum of var explained"), shape = 18, size = 4) +
   ## Themes, legends and colors 
   theme_minimal() +
   labs(title = "pca screeplot of normalized flea data",
        x = "Component number", 
        y = "Variance explained",
        colour = "", fill = "") + 
   # theme(legend.position = c(0.9, 0.5)) + ## legend position doesn't work now because different geoms??
   scale_fill_manual(values = "#1B9E77") + 
   scale_colour_manual(values = "#D95F02"))
# RColorBrewer::brewer.pal(n=2, "Dark2")
```

The user study task trys to explore the *full sample, full dimensionality* $[n,p]$ seperation of two specified clusters. In an analogous manner, let's try to create a screeplot-like output to evalute the contributions of the original variables.

```{r lda}
DO_RUN <- FALSE
if (DO_RUN) {
  .cl  <- unique(class)[1:2]
  .sub <- dat[class == .cl, ]
  .lda_dat <- data.frame(.sub, species = class[class == .cl]) 
  
  library(MASS)
  (lda_obj <- lda(species~., data = .lda_dat))
}
```

Because Linear Discriminant Analysis (LDA) used cluster means and not their medians, we'll select mean as well. Let's find the $p$-space cluster means.

```{r clusterMeans}
df_clusterMeans <- NULL
for (i in 1:k_cl) {
  .cl  <- unique(class)[i]
  .sub <- dat[class == .cl, ]
  .row <- apply(.sub, 2, mean)
  df_clusterMeans <- rbind(df_clusterMeans, .row)
}
df_clusterMeans <- as.data.frame(df_clusterMeans, row.names = unique(class))
kable(df_clusterMeans)
``` 

Suppose the clusters in questions are *Concinna* and *Heptapot*, now let's find the $p$-dim line between their means. Let of the cluster mean of *Concinna* be the $p$-dim constant vetor. Then $p$-dim slope is then 

```{r lineCoeff}
.cl_mns   <- df_clusterMeans[1:2, ]
.constant <- .cl_mns[1,] 
rownames(.constant) <- ("constants_ConcinnaHeptapot")
.coeff    <-  - (.cl_mns[2,] - .cl_mns[1,])
rownames(.coeff) <- ("coefficients_ConcinnaHeptapot")
kable(rbind(.constant, .coeff))
``` 

We have a vector of variable-coffecients corisponding to the sepration of the cluster means. Let's discard the orientation. The remaining magnitudes describe the *full sample, full dimensionality* seperation of the cluster means between *Concinna* and *Heptapot*. Let's visualize This similar to the screeplot.

```{r clSepScreeplot}
.mag <- abs(.coeff)
.clSep_rate <- t(.mag[order(.mag, decreasing = T)]) / sum(.mag)
.var_nm_ord <- factor(row.names(.clSep_rate), levels=unique(row.names(.clSep_rate)))

df_clSep <- data.frame(variable = .var_nm_ord,
                       rate_clSep = as.vector(.clSep_rate),
                       cumsum_rate_clSep = cumsum(.clSep_rate))

(g2 <- ggplot(data = df_clSep) + 
    ## Individual clSep bars
    geom_bar(stat = "identity", 
             mapping = aes(x = variable, y = rate_clSep, 
                           fill = "Individual clSep explained")) + 
    ## Cummulative clSep line
    geom_line(mapping = aes(x = variable, y = cumsum_rate_clSep, group = 1,
                            color = "Cumsum of clSep explained"), lwd = 1.2) +
    geom_point(mapping = aes(x = variable, y = cumsum_rate_clSep,
                             color = "Cumsum of clSep explained"), shape = 18, size = 4) +
    ## Themes, legends and colors 
    theme_minimal() +
    labs(title = "Variables contributions to the seperation of cluster means [Concinna-Heptapot]",
         x = "Variable", 
         y = "Seperation of cluster means", 
         colour = "", fill = "") + 
    # theme(legend.position = c(0.9, 0.5)) + ## legend position doesn't work now because different geoms??
    scale_fill_manual(values = "#1B9E77") + 
    scale_colour_manual(values = "#D95F02"))
# RColorBrewer::brewer.pal(n=2, "Dark2")
```