---
title: "Mixed model regression"
author: "Nick Spyrison"
date: "11/03/2021"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
header-includes:
   - \usepackage{amsmath}
   - \usepackage{showframe}
editor_options:
  chunk_output_type: console
---
```{r setup, include=FALSE}
library("tidyverse")
library("ggpubr") ## for tests on the plot
library("cowplot") ## for aggregating plots
library("lme4") ## Random Effects (RE) model creation
library("lmerTest") ## p val interpretation of lme4 tests
library("merTools")
library("performance") ## tidy model eval
library("plyr")
library("dplyr")

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
rel_path <- function(rel_path = "."){
  rel_dir  <- dirname(rstudioapi::getSourceEditorContext()$path)
  rel_path <- paste0(rel_dir, "/", rel_path)
  normalizePath(rel_path, winslash = "/")
}

## Portrait dim, inside margin
.u = "in"
.w = 6.25
.h = 9
```
```{r LOAD_FORMAT_LOCAL_FUNCS}
## Load raw data, clean, and save
if(FALSE){
  source("./paper/R/9_util_funcs.r") ## previously ggproto_pca_biplot.r
  raw <- readRDS(rel_path("../data_study/raw.rds"))
  ## Only plot_active rows 
  ## AND Only participants (rows where nchar(Participant) == 24 charcters long)
  dat_active <- raw %>% filter(nchar(stringr::str_trim(prolific_id)) == 24)
  ## pivot variables columns longer; each row is 1 variable
  dat_longer <- pivot_longer_resp_ans_tbl(dat_active)
  ## Impute missing sec_to_resp, via mean diff with sec_on_pg, only 20 rows in 8330
  .mean_pg_resp_diff <- mean(dat_longer$sec_on_pg, na.rm = TRUE) -
    mean(dat_longer$sec_to_resp, na.rm = TRUE)
  dat_longer <- dat_longer %>%
    mutate(sec_to_resp = if_else(
      is.na(sec_to_resp), sec_on_pg - .mean_pg_resp_diff, sec_to_resp))
  ## Aggregate to task grain.
  dat_task_agg <- aggregate_task_vars(dat_longer) %>%
    ## Fix observeEvent() over count of radial input_inter.
    mutate(
      task_input_inter = if_else(
        factor == "radial", task_input_inter -1, task_input_inter)) %>%
    ## Plot friendly titles
    mutate(prolific_id = stringr::str_trim(prolific_id),
           instance_id = paste(
             sep = "_", participant_num, full_perm_num, prolific_id),
           factor = factor(factor, levels = c("pca", "grand", "radial"))
    ) %>%
    dplyr::rename(simulation = sim_nm,
           shape = vc,
           dim = p_dim,
           order = eval,
           participant = prolific_id,
           `is training` = is_training,
           `# response interactions` = task_resp_inter,
           `seconds to last response` = max_sec_to_resp,
           `seconds on page` = max_sec_on_pg,
           `# of responses` = cnt_resp,
           marks = task_marks,
           `parameter permutation` = full_perm_num)
  ## Check same as raw.rds support; factor aggregation of Marks
  dat_task_agg %>%
    dplyr::select(factor, marks) %>%
    dplyr::group_by(factor) %>%
    dplyr::summarise(mean = mean(marks),
                     sd   = sd(marks),
                     min  = min(marks),
                     max  = max(marks))
  ## GOOD; Same as raw.rds; NOTE that this is all data, training, partial instances, and over evaled permutations
  ## Save task aggregated data.
  saveRDS(dat_task_agg, rel_path("../data_study/dat_task_agg.rds"))
}
## load aggregated data.
dat_task_agg <- readRDS(rel_path("../data_study/dat_task_agg.rds"))
## filter out raining data for now; is even eval is the new color/fill go to.
dat_task_agg <- dat_task_agg %>%
  filter(`is training` == FALSE) %>%
  ## Display capitalization
  dplyr::rename(
    Participant = participant,
    Simulation  = simulation, 
    Factor      = factor,
    Shape       = shape,
    Dim         = dim,
    Location    = location,
    Marks       = marks)

## Local functions -----

## direct ggplot2 helpers
my_theme <- list(
  theme_bw(),
  scale_color_brewer(palette = "Dark2"),
  scale_fill_brewer(palette = "Dark2"),
  geom_hline(yintercept = 0L),
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.margin = margin(-6L))
)

## indirect (via ggpubr/cowplot) ggplot2 helpers
#' @examples
#' df=dat_qual;x="factor";y="marks";title = waiver(); subtitle = waiver(); facet = NULL
my_ggpubr <- function(
  df, x = "Factor", y = "Marks",
  title = waiver(), subtitle = waiver(), facet = NULL,
  y_pval_coef = .08,  ## Subjective wants .032
  ylim_max_coef = .5 ## Subjective wants .6
){
  ## Find height of global significance test text.
  .x_lvls <- df %>% pull({{x}}) %>% levels()
  .y <- df %>% pull({{y}})
  if(is.factor(.y)) .y <- as.integer(.y)
  .y_range <- diff(range(.y))
  .no_x_lvls <- length(.x_lvls)
  if(is.null(facet) == FALSE){
    .facet_lvls <- df %>% pull({{facet}}) %>% levels() %>% length()
  } else .facet_lvls <- 1 ## Init
  .lab.y <- (y_pval_coef * .y_range) * (1 + .no_x_lvls) * .y_range + max(.y) 
  my_comparisons <- NULL
  if(.no_x_lvls == 2)
    my_comparisons <- list(c(.x_lvls[1], .x_lvls[2]))
  if(.no_x_lvls == 3)
    my_comparisons <- list(c(.x_lvls[1], .x_lvls[2]),
                           c(.x_lvls[2], .x_lvls[3]),
                           c(.x_lvls[1], .x_lvls[3]))
  
  ## Plot
  ggviolin(df, x = x, y = y, fill = x, alpha = .6,
           palette = "Dark2", shape = x, trim = TRUE,
           add = c("mean"), ## Black circle, can change size, but not shape or alpha?
           draw_quantiles = c(.25, .5, .75)) +
    stat_compare_means(label.y = .lab.y,
                       aes(label = paste0("p = ", ..p.format..)), ## Global test
                       hide.ns = TRUE) + ## custom label
    stat_compare_means(method = "wilcox.test", ## pairwise test
                       comparisons = my_comparisons,
                       label = "p.signif", hide.ns = TRUE) +
    my_theme +
    coord_cartesian(ylim = c(min(.y), max(.y) + ylim_max_coef * .y_range)) +
    ggtitle(title, subtitle) +
    ggplot2::xlab(paste0(
      x, "\n(n=", nrow(df)/(.no_x_lvls * .facet_lvls), " each)"))
}
my_ggpubr_facet <- function(..., facet = "Location"){
  facet(my_ggpubr(..., facet = facet), facet.by = facet)
}
```
  
______
  
# Results

## Filter to 3 most recent block evaluations


```{r}
#### Aggregation tables
## instance_agg; instance is 1 trial
instance_agg <- dat_task_agg %>%
  group_by(instance_id, participant_num, `parameter permutation`, Participant) %>%
  dplyr::summarise(`n instance evals` = n() / 6) %>%
  ungroup() %>%
  mutate(is_instance_even = if_else(`n instance evals` == 1, TRUE, FALSE)) %>%
  arrange(desc(`n instance evals`))
## Find vector of evenly evaled instance_ids
instance_id_is_even_whitelist <- instance_agg %>%
  filter(is_instance_even == TRUE) %>%
  pull(instance_id)
## Decode the original dataset by evenness of instance_id.
dat_qual <- dat_task_agg %>%
  mutate(`is even instance` =
           if_else(instance_id %in% instance_id_is_even_whitelist, TRUE, FALSE))


## participant aggregate table
participant_agg <- dat_qual %>%
  group_by(Participant, `is even instance`) %>%
  dplyr::summarise(`even evaluations` = n() / 6) %>%
  ungroup() %>%
  arrange(desc(`even evaluations`))
## perm_num aggregate table
perm_num_agg <- dat_qual %>%
  group_by(`parameter permutation`, `is even instance`) %>%
  dplyr::summarise(`even evaluations` = n() / 6) %>%
  ungroup() %>%
  arrange(desc(`even evaluations`))

#### Identify and remove instances with over evaled perms AND participants.
## Identify participants that have performed more than 1 even eval from
participant_blacklist <- participant_agg %>%
  group_by(Participant) %>%
  dplyr::summarise(`even evaluations` = sum(`even evaluations`)) %>%
  ungroup() %>%
  filter(`even evaluations` > 1) %>%
  pull(Participant)
## Identify over evaled perm numbers
perm_num_blacklist <- perm_num_agg %>%
  filter(`is even instance` == TRUE,
         `even evaluations` > 3) %>%
  pull(`parameter permutation`)
## instance_id's in all surveys
survey_wider <- readRDS(rel_path("../data_survey/survey_wider.rds"))
instance_id_in_survey <- unique(survey_wider$instance_id)

## Decode the original dataset by evenness of instance_id.
dat_qual <- dat_qual %>%
  mutate(is_particiapnat_blacklisted =
           if_else(Participant %in% participant_blacklist, TRUE, FALSE),
         is_perm_num_blacklisted =
           if_else(`parameter permutation` %in% perm_num_blacklist, TRUE, FALSE),
         is_instance_id_in_survey =
           if_else(instance_id %in% instance_id_in_survey, TRUE, FALSE),
         removal_priority = if_else(is_instance_id_in_survey == TRUE, -1L,
           is_particiapnat_blacklisted + is_perm_num_blacklisted),
         perm_prolific_id = paste(sep = "_", `parameter permutation`, Participant))

## Identify the final results to keep as prioritized with the first 3 evals of:
#### arrange(`parameter permutation`, removal_priority, desc(write_dt))
#### where removal_priority get 1 each for perm and participant being over evaled.
instance_id_whitelist <- dat_qual %>%
  dplyr::filter(`is even instance` == TRUE) %>%
  arrange(`parameter permutation`, removal_priority) %>% #,desc(write_dt)) %>%
  group_by(`parameter permutation`, instance_id) %>%
  dplyr::summarise(`even evaluations` = 1) %>%
  dplyr::mutate(wi_perm_instance_rn = 1:n()) %>%
  dplyr::filter(wi_perm_instance_rn < 4) %>%
  pull(instance_id)
 
## Apply the final white list, the last 3 even evaluations of each perm
.lvls = c("0/100%", "33/66%", "50/50%")
dat_qual <- dat_qual %>%
  filter(instance_id %in% instance_id_whitelist) %>% 
  mutate(Location = factor(
    .lvls[as.integer(Location)], levels = .lvls)
  )

if(interactive())
  saveRDS(dat_qual, rel_path("../data_study/dat_qual.rds"))

N <- length(unique(dat_qual$instance_id))
print(paste0("N = ", N, " unique instance_id."))

## Evaluation by parameter permutations with candidates removed
print("After evaluating the evenness of participants, permutations, the probability of adverse network interactions we have selected 3 evaluations of each block permutation to perfom the analysis on:")
print("Note: Training removed, partial evaluations removed, only the evaluations of the remaining instances.")

#### Now update perm agg and plot
perm_num_agg2 <- dat_qual %>%
  group_by(`parameter permutation`, `is even instance`) %>%
  dplyr::summarise(`even evaluations` = n() / 6) %>%
  ungroup()

(gg_eval_by_perm_num_removed <- perm_num_agg2 %>%
    ggplot(aes(x = `parameter permutation`, y = `even evaluations`,
               color = `is even instance`, fill = `is even instance`)) +
  labs(
    title = "Evaluations by parameter permutaion", 
    subtitle = "Remaining set of data, 3 evaluations of all block parameter permutations") +
  my_theme +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 3, linetype = 2) +
  geom_text(aes(x = 33, y = 3.1, label = "target"), color = "black")
)
  
## Check w.r.t. raw.rds; different means but we have removed training, partial instances and over sample permutations. Support is still realistic.
dat_qual %>% dplyr::select(Factor, Marks) %>%
  group_by(Factor) %>%
  dplyr::summarise(
    min  = min(Marks),
    max  = max(Marks),
    mean = mean(Marks),
    median = median(Marks))
```


## Mixed, random effect regression

_Context: 648 task evaluations from 108 studies; we regress against marks using block parameters_

See the paper for latex terminology, but keep in mind:

\begin{align*}
&\alpha~is~factor \\
&\beta~is~location \\
&\gamma~is~shape \\
&\delta~is~dim
\end{align*}

```{r}
{ ## Load local functions, abstracting code complexity
  ## Print coef of the model that are greater than selected t_val
  mod_coef_gt_t <- function(mod, gt_t = 1.5){
    .coef <- summary(mod)$coefficients %>% data.frame() ## tibble failed
    .coef %>% filter(abs(t.value) > gt_t)
  }
  mod_anova_gt_f <- function(mod, gt_f = 1){
    .anova <- anova(mod) %>% data.frame() ## tibble failed
    .anova %>% filter(abs(F.value) > gt_f)
  }
  ## A qq plot of the Random Effect simulation
  plot_REsim_qq <- function(model){
    .df <- data.frame(y = REsim(model)$mean)
    ggplot(.df, aes(sample = y)) +
      stat_qq(alpha = .5) + stat_qq_line() + my_theme +
      ggtitle("qq plot of the mean of random effects simulation")
  }
  ## Adds kable markup to bold the max/min of a column.
  format_column_extrema <- function(df, col, extrema = max, markup = "*"){
    ## c("*", "**", "~~"), c("italics", "bold", "strikethrough")
    v <- as.data.frame(df[, col])[, 1]
    ## Make sure values are not factors
    r_idx <- which(v == extrema(v))
    ## Update formatting
    v[r_idx] <- paste0(markup, v[r_idx], markup)
    df[, col] <- v
    return(df)
  }
  ## Summarizes data.
  ## Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
  ##   data: a data frame.
  ##   measurevar: the name of a column that contains the variable to be summariezed
  ##   groupvars: a vector containing names of columns that contain grouping variables
  ##   na.rm: a boolean that indicates whether to ignore NA's
  ##   conf.interval: the percent range of the confidence interval (default is 95%)
  if(FALSE)
    browseURL("http://www.cookbook-r.com/Manipulating_data/Summarizing_data/")
  summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                        conf.interval=.95, .drop=TRUE){
    # New version of length which can handle NA's: if na.rm==T, don't count them
    
    length2 <- function (x, na.rm=FALSE){
      if (na.rm) sum(!is.na(x))
      else       length(x)
    }
    
    # This does the summary. For each group's data frame, return a vector with
    # N, mean, and sd
    datac <- ddply(data, groupvars, .drop=.drop,
                   .fun = function(xx, col){
                     c(N    = length2(xx[[col]], na.rm=na.rm),
                       mean = mean   (xx[[col]], na.rm=na.rm),
                       sd   = sd     (xx[[col]], na.rm=na.rm)
                     )
                   },
                   measurevar
    )
    
    # Rename the "mean" column    
    datac <- rename(datac, c("mean" = measurevar))
    
    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
    
    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult
    
    return(datac)
  }
  ## Extracts the coefficients of a model and applies stars.
  model2coef <- function(model){
    summary(model)$coefficients %>% data.frame(check.names = F) %>%
      mutate(" " = case_when(`Pr(>|t|)` < .001 ~ "***",
                             `Pr(>|t|)` < .01 ~ "**",
                             `Pr(>|t|)` < .05 ~ "*",
                             TRUE ~ ""))
  }
}

## Mixed (fixed and random/variable) effects regression model
### following along with:
if(FALSE) 
  browseURL("https://m-clark.github.io/mixed-models-with-R/random_intercepts.html#running-a-mixed-model")

############################
#### CREATE MODELS -----
############################
# a == factor, b == location, c == shape, d == dim
## The Models:
a    <- lmer(Marks ~ Factor + (1 | Participant) + (1 | Simulation), data = dat_qual)
abcd <- lmer(Marks ~ Factor + Location + Shape + Dim + (1 | Participant) + (1 | Simulation), data = dat_qual)
ABcd <- lmer(Marks ~ Factor * Location + Shape + Dim + (1 | Participant) + (1 | Simulation), data = dat_qual)
ABCd <- lmer(Marks ~ Factor * Location * Shape + Dim + (1 | Participant) + (1 | Simulation), data = dat_qual)
ABCD <- lmer(Marks ~ Factor * Location * Shape * Dim + (1 | Participant) + (1 | Simulation), data = dat_qual)
model_ls <-list(a=a, abcd=abcd, ABcd=ABcd, ABCd=ABCd, ABCD=ABCD)

############################
#### COMPARE  MODELS -----
############################
## lapply over models
performance_ls <- list(); factors_vec <- fixef_vec <- vector();
mute <- lapply(seq_along(model_ls), function(i){
  this_model <- model_ls[[i]]
  performance_ls[[i]] <<- performance::model_performance(this_model)
  factors_vec[i] <<- ncol(attr(terms(this_model), "factors"))
  fixef_vec[i] <<- length(fixef(this_model))
})
.perf_df <- dplyr::bind_rows(performance_ls)
.model_comp_colnms <- c("Fixed effects", "No. levels", "No. terms",
                        "AIC", "BIC", "R2 cond.", "R2 marg.", "RMSE")
model_comp_tbl <- tibble(names(model_ls),
                         factors_vec,
                         fixef_vec,
                         round(.perf_df[, 1]),
                         round(.perf_df[, 2]),
                         round(.perf_df[, 3], 3),
                         round(.perf_df[, 4], 3),
                         round(.perf_df[, 6], 3),
)
colnames(model_comp_tbl) <- .model_comp_colnms

## print table
knitr::kable(model_comp_tbl)
# a == factor, b == location, c == shape, d == dim

############################
#### EXPLORE SELECTED MODEL ----
############################
ABcd_coef <- model2coef(ABcd)
ABcd
ggEffectRanges <- plotREsim(REsim(ABcd)) +
  ggtitle(label = "", subtitle = "Accuracy model: Y1^ = \u03b1 * \u03b2 + \u03b3 + \u03b4      confidence: \u03b1 = .95") +
  theme(axis.title.x = element_blank()) +
  labs(y = "Effect range")

#### If you want to show boxplots cannot aggregate over evaluation, 
## By participant
participant_agg <- summarySE(dat_qual, "Marks", "Participant") %>%
  mutate(Participant = forcats::fct_reorder(Participant, Marks))
ggParticipantRanges <- ggplot(participant_agg) +
  geom_point(aes(Participant, Marks), alpha = .2, size = 2) +
  geom_linerange(aes(Participant, ymin = Marks - ci, ymax = Marks + ci), alpha = .3) +
  my_theme +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_cartesian(ylim = c(-1, 1)) +
  ylab("CI mean marks") +
  xlab("Participant (n=6 each)")
ggParticipantRanges <-
  ggExtra::ggMarginal(ggParticipantRanges, type = "density", fill = "grey80")
## By simulation
simulation_agg <- summarySE(dat_qual, "Marks", "Simulation") %>%
  mutate(Simulation = forcats::fct_reorder(Simulation, Marks))
ggSimulationRanges <- ggplot(simulation_agg) +
  geom_point(aes(Simulation, Marks), alpha = .2, size = 2) +
  geom_linerange(aes(Simulation, ymin = Marks - ci, ymax = Marks + ci), alpha = .3) +
  my_theme +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_cartesian(ylim = c(-1, 1)) +
  xlab("Simulation (n=36 each)")
ggSimulationRanges <-
  ggExtra::ggMarginal(ggSimulationRanges, type = "density", fill = "grey80")
## Bringing it all together
botCis <-
  cowplot::plot_grid(ggParticipantRanges, 
                     ggSimulationRanges,
                     ncol = 2, rel_widths = c(1.07, 1))

(figEffectRange <- cowplot::plot_grid(ggEffectRanges, botCis, nrow = 2))
```

## Violin plot of models

### Model alpha

```{r}
(marks_by_factor <-
   my_ggpubr(dat_qual,
             x = "Factor", y = "Marks",
             title = "Accuracy by factor")) + ylab("Accuracy")
```

### Model alpha * beta + gamma + delta

```{r}
.lp <- theme(legend.position = "off", 
             plot.margin = ggplot2::unit(c(6,3,3,0), "points"))
.ynums <- theme(axis.ticks.y = element_blank(), axis.text.y = element_blank())
.yl <- ylab("")
if(interactive())
  saveRDS(dat_qual, "./dat_qual.rds")
.factor   <- my_ggpubr(dat_qual, x = "Factor", y = "Marks") + .lp + ylab("Accuracy")
.lvls     <- c("0/100%", "33/66%", "50/50%")
dat_qual  <- dat_qual %>%
  mutate(Location = factor(.lvls[as.integer(Location)], levels = .lvls))
levels(dat_qual$Location)
.location <- my_ggpubr(dat_qual, x = "Location", y = "Marks") + .lp + .yl + .ynums
.shape    <- my_ggpubr(dat_qual,     x = "Shape",    y = "Marks") + .lp + .yl + .ynums
.dim      <- my_ggpubr(dat_qual,     x = "Dim",      y = "Marks") + .lp + .yl + .ynums
.FactorLocation <- my_ggpubr_facet(
  dat_qual, x = "Factor", y = "Marks", facet = "Location") + ylab("Accuracy")

title <- cowplot::ggdraw() +
  cowplot::draw_label(
    "Violin plots of the terms for accuracy: Y1^ = \u03b1 * \u03b2 + \u03b3 + \u03b4", 
    x = .5, y = .75, hjust = .5, vjust = 1)
top <- cowplot::plot_grid(
  .factor, .location, .shape, .dim, nrow = 1, rel_widths = c(1.15, 1, 1, 1))
.m <- gc()
(violin_ABcd <-
  cowplot::plot_grid(title, top, .FactorLocation + ggtitle("", ""),
                     ncol = 1, rel_heights = c(.1, 1, 1.4)))
```


## Regression agianst time

As a secondary explanatory variable we also want to look at time. First we take the log transformation of time as it is right skewed. Now we repeat the same modeling procedure, namely, 1) build a battery of all additive and multiplicative models. 2) Compare their performance, reporting a some top performers.
3) Select a model to examine it's coefficients.

```{r}
## Once again, abbreviated verse regressing on time.
############################
#### CREATE -----
############################
## a == factor
## b == location
## c == shape
## d == dim
## Take log of right skewed time.
dat_qual <- dat_qual %>%
  mutate(log_sec_last_resp = log(`seconds to last response`))
## The Models:
ta    <- lmer(log_sec_last_resp ~ Factor + (1 | Participant) + (1 | Simulation), data = dat_qual)
tabcd <- lmer(log_sec_last_resp ~ Factor + Location + Shape + Dim + (1 | Participant) + (1 | Simulation), data = dat_qual)
tABcd <- lmer(log_sec_last_resp ~ Factor * Location + Shape + Dim + (1 | Participant) + (1 | Simulation), data = dat_qual)
tABCd <- lmer(log_sec_last_resp ~ Factor * Location * Shape + Dim + (1 | Participant) + (1 | Simulation), data = dat_qual)
tABCD <- lmer(log_sec_last_resp ~ Factor * Location * Shape * Dim + (1 | Participant) + (1 | Simulation), data = dat_qual)
t_model_ls <- list(
  ta = ta, tabcd = tabcd, tABcd = tABcd, tABCd = tABCd, tABCD = tABCD)

############################
#### COMPARE -----
############################
## lapply over models
t_performance_ls <- list(); t_factors_vec <- t_fixef_vec <- vector()
mute <- lapply(seq_along(t_model_ls), function(i){
  this_model <- t_model_ls[[i]]
  t_performance_ls[[i]] <<- performance::model_performance(this_model)
  t_factors_vec[i] <<- ncol(attr(terms(this_model), "factors"))
  t_fixef_vec[i] <<- length(fixef(this_model))
})
.t_perf_df <- dplyr::bind_rows(t_performance_ls)
t_model_comp_tbl <- tibble::tibble(names(t_model_ls),
                                   t_factors_vec,
                                   t_fixef_vec,
                                   round(.t_perf_df[, 1]),
                                   round(.t_perf_df[, 2]),
                                   round(.t_perf_df[, 3], 3),
                                   round(.t_perf_df[, 4], 3),
                                   round(.t_perf_df[, 6], 3))
colnames(t_model_comp_tbl) <- .model_comp_colnms

## print model comparison table
knitr::kable(t_model_comp_tbl)
############################
#### EXPLORE ----
############################
## Explore selected model, log sec to resp ~ ABC
t_ABcd_coef <- model2coef(tABcd)
knitr::kable(t_ABcd_coef)

## Redefine my_theme to remove line at y = 0.
my_theme <- list(
  theme_bw(),
  scale_color_brewer(palette = "Dark2"),
  scale_fill_brewer(palette = "Dark2"),
  #geom_hline(yintercept = 0L),
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.margin = margin(-6))
)

ggEffectRanges <- plotREsim(REsim(tABcd)) +
  ggtitle("", subtitle="Log response time [seconds] model: Y2^ = \u03b1 * \u03b2 + \u03b3 + \u03b4      confidence: \u03b1 = .95") +
  theme(axis.title.x = element_blank()) +
  ylab("Effect range")

## By participant
participant_agg <- summarySE(dat_qual, "log_sec_last_resp", "Participant") %>%
  mutate(Participant = forcats::fct_reorder(Participant, log_sec_last_resp ))
ggParticipantRanges <- ggplot(participant_agg) +
  geom_point(aes(Participant, log_sec_last_resp), alpha = .2, size = 2) +
  geom_linerange(aes(Participant, ymin = log_sec_last_resp  - ci,
                     ymax = log_sec_last_resp + ci), alpha = .3) +
  my_theme +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  geom_hline(yintercept = mean(participant_agg$log_sec_last_resp)) +
  xlab("Participant (n=6 each)") +
  ylab("CI mean log last response [seconds]")
ggParticipantRanges <-
  ggExtra::ggMarginal(ggParticipantRanges, type = "density", fill = "grey80")
## By simulation
simulation_agg <- summarySE(dat_qual, "log_sec_last_resp", "Simulation") %>%
  mutate(Simulation = forcats::fct_reorder(Simulation, log_sec_last_resp))
ggSimulationRanges <- ggplot(simulation_agg) +
  geom_point(aes(Simulation, log_sec_last_resp), alpha = .2, size = 2) +
  geom_linerange(aes(Simulation, ymin = log_sec_last_resp - ci,
                     ymax = log_sec_last_resp + ci), alpha = .3) +
  my_theme +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  geom_hline(yintercept = mean(simulation_agg$log_sec_last_resp)) +
  xlab("Simulation (n=36 each)")
ggSimulationRanges <-
  ggExtra::ggMarginal(ggSimulationRanges, type = "density", fill = "grey80")
## Bringing it all together
botCis <-
  cowplot::plot_grid(ggParticipantRanges, ggSimulationRanges,
                     ncol = 2, rel_widths = c(1.07, 1))
(t_figEffectRange <- cowplot::plot_grid(ggEffectRanges, botCis, nrow = 2))
```

______

# Saving paper figures (interactive only)

Note that knitting .rmd file does not save figures and .rds files while interactive run all chunks will save new figures and .rds files.
```{r}
if(interactive()){
  ## instance_id whitelist, the people kept for analysis.
  #### (instance_id is: participant_num "_" perm_num "_" prolific_id)
  saveRDS(instance_id_whitelist,
          file = "./paper/data_study/instance_id_whitelist.rds")
  
  ## Model table
  rownames(model_comp_tbl) <- rownames(t_model_comp_tbl) <- NULL
  mod_comp <- list(modelComp_MarksByEval = model_comp_tbl,
                   modelComp_TimeByEval = t_model_comp_tbl)
  mod_comp[[1]]$`Fixed effects` <- mod_comp[[2]]$`Fixed effects` <-
    c("a", "a+b+c+d", "a*b+c+d", "a*b*c+d", "a*b*c*d")
  
  require(kableExtra)
  ### Attempt to format cell_spec(), have to split format here...
  format_cells <- function(
    df, rows, cols, bold = T, format = "latex", ...
  ){
    df <- as.data.frame(df) ## tibbles not allowed
    for(i in seq_along(rows)){
      df[[cols[i]]] <- as.character( df[[cols[i]]])
      df[rows[i], cols[i]] <- kableExtra::cell_spec(
        df[rows[i], cols[i]], format = format, bold = bold, ...)
    }
    df
  }
  
  c_idx <- 4:8 ## AIC   BIC `R2 cond.` `R2 marg.`  RMSE
  ## Accuracy model
  r_idx <- c(
    which(mod_comp[[1]]$AIC        == min(mod_comp[[1]]$AIC)),
    which(mod_comp[[1]]$BIC        == min(mod_comp[[1]]$BIC)),
    which(mod_comp[[1]]$`R2 cond.` == max(mod_comp[[1]]$`R2 cond.`)),
    which(mod_comp[[1]]$`R2 marg.` == max(mod_comp[[1]]$`R2 marg.`)),
    which(mod_comp[[1]]$RMSE       == min(mod_comp[[1]]$RMSE))
  )
  ## html copy for thesis
  mod_comp_html <- mod_comp
  ## TeX
  mod_comp[[1]] <- format_cells(
    mod_comp[[1]], rows = r_idx, cols = c_idx, bold = T)
  ## HTML
  mod_comp_html[[1]] <- format_cells(
    mod_comp_html[[1]], rows = r_idx, cols = c_idx, bold = T, format = "html")
  
  ## Log time model
  r_idx <- c(
    which(mod_comp[[2]]$AIC        == min(mod_comp[[2]]$AIC)),
    which(mod_comp[[2]]$BIC        == min(mod_comp[[2]]$BIC)),
    which(mod_comp[[2]]$`R2 cond.` == max(mod_comp[[2]]$`R2 cond.`)),
    which(mod_comp[[2]]$`R2 marg.` == max(mod_comp[[2]]$`R2 marg.`)),
    which(mod_comp[[2]]$RMSE       == min(mod_comp[[2]]$RMSE))
  )
  ## TeX
  mod_comp[[2]] <- format_cells(
    mod_comp[[2]], rows = r_idx, cols = c_idx, bold = T)
  ## HTML
  mod_comp_html[[2]] <- format_cells(
    mod_comp_html[[2]], rows = r_idx, cols = c_idx, bold = T, format = "html")
  ## Tex copy for this paper
  saveRDS(mod_comp, file = "./paper/figures/modelCompLs.rds")
  ## Save a Latex copy for thesis_ns
  saveRDS(mod_comp, file = "../thesis_ns/figures/ch4_tab1_model_comp_ls_latex.rds")
  ## Save a html copy for thesis_ns
  saveRDS(mod_comp_html, file = "../thesis_ns/figures/ch4_tab1_model_comp_ls_html.rds")
  
  ## Model coefficients: marks ~ ABcd, log_sec_to_resp ~ ABC
  round_coef <- function(coef_df){
    coef_df[,  5] <- round(coef_df[,  5], 3) ## Pr(>|t|)
    coef_df[, -c(5, 6)] <- round(coef_df[, -c(5, 6)], 2) ## Except for Pr(>|t|), and stars
    coef_df[, 3]  <- round(coef_df[, 3], 1)  ## further round degrees of freedom
    coef_df
  }
  coef_ls <- list(ABcd_coef = round_coef(ABcd_coef),
                  t_ABcd_coef = round_coef(t_ABcd_coef))
  ## Save for this paper
  saveRDS(coef_ls, file = "./paper/figures/modelCoefLs.rds")
  ## Save a copy for thesis_ns
  saveRDS(mod_comp, file = "../thesis_ns/figures/ch4_tab2_model_coef_ls.rds")
  
  ## RE Effect ranges by CI of mean marks
  ggsave("figEffectRange.pdf", plot = figEffectRange, path = "./paper/figures",
         device = cairo_pdf, width = .w, height = .w, unit = .u)
  ggsave("figTeffectRange.pdf", plot = t_figEffectRange, path = "./paper/figures",
         device = cairo_pdf, width = .w, height = .w, unit = .u)
  
  ## Marks by violin of factor faceting on location and shape
  ggsave("figMarksABcd.pdf", violin_ABcd, path = "./paper/figures",
         device = cairo_pdf, width = .w, height = .w, unit = .u)
}
.m <- gc()
```

